%-------------------------
% CV in LaTeX
% Author : Victor Verma
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Large \scshape Victor Verma} \\ \vspace{1pt}
    \href{mailto:victor.verma@hotmail.com}{\underline{victor.verma@hotmail.com}} $|$ 
    \href{https://www.victorverma.com}{\underline{victorverma.com}} $|$ 
    \href{https://linkedin.com/in/victorverma/}{\underline{linkedin.com/in/victorverma}} $|$
    \href{https://github.com/victorverma3}{\underline{github.com/victorverma3}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Boston University}{Boston, MA}
      {B.A. in Mathematics \& Computer Science, Minor in Data Science}{May 2025}
      \resumeItemListStart
        \resumeItem{\textbf{Honors/Activities:} Magna Cum Laude, 3.89 GPA, Dean’s List, Kappa Theta Pi, Men’s Rugby. }
        \resumeItem{\textbf{Relevant Courses:} Machine Learning and AI, Data Science Tools and Applications, Natural Language Processing, Stochastic Algorithms, Stochastic Processes, Probability, Linear Algebra, Multivariate Calculus, Algorithms, Differential Equations, Database Systems, Computing Systems, Engineering for Big Data, Software Engineering. }
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------WORK EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {Savvas Learning Company}{Boston, MA}
      {Associate Software Developer}{Jun 2025 - Present}
      \resumeItemListStart
      	\resumeItem{Developed an \textbf{XLM-RoBERTa} model to classify sentence types in K-12 writing (\textbf{0.89 F1}), reducing LLM annotation costs by \textbf{33\%} when balancing training datasets for other internal models.}
	\resumeItem{Optimized a sentence fragment detection model (\textbf{0.85 F1}) by designing tooling infrastructure to synthetically label the sentence type, English quality, and fragmentation of \textbf{25,000+} training sentences using \textbf{Amazon Bedrock}.}
        \resumeItem{Implemented a \textbf{FastMCP} server for GitHub Copilot, enabling Savvas engineers to seamlessly export their codebase context to Google Gemini in under \textbf{20 seconds} for AI assistance.}
      	\resumeItem{Improved the latent space separability of supporting evidence embeddings across 6 subcategories, measured by the cosine similarity of their respective centroids, by balancing the pairwise comparisons training dataset through Jensen-Shannon-informed downsampling and probabilistic upsampling.}
      \resumeItemListEnd
      
      \resumeSubSubheading
      {Software Development Engineering Intern}{Jun 2024 - Aug 2024}
      \resumeItemListStart
        \resumeItem{Developed a \textbf{ReAct agent} allowing Savvas employees to efficiently query internal Confluence documentation and GitHub codebases, utilizing \textbf{Python}, \textbf{Amazon Bedrock}, and the \textbf{LlamaIndex API}.}
        \resumeItem{Constructed a comprehensive knowledge base for the chatbot and automated the upload of \textbf{500+} Confluence documents and GitHub README files to \textbf{S3 buckets} using the Confluence and GitHub APIs.}
        \resumeItem{Launched the ReAct agent as a service using \textbf{AWS Lambda}, featuring a \textbf{Gradio} frontend and \textbf{FastAPI} backend, and configured role-based access for employees through \textbf{Google OAuth}.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------RESEARCH EXPERIENCE-----------
\section{Research Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Boston University}{Boston, MA}
      {Research Assistant $|$ \href{https://github.com/victorverma3/Undergraduate-Research/tree/main/state_medical_boards}{\underline{Identifying Physician Discipline Trends with NLP}}}{Aug 2024 - May 2025}
      \resumeItemListStart
        \resumeItem{Trained and evaluated \textbf{DSPy chain-of-thought programs} to flag disciplinary violations (malpractice, fraud, improper prescriptions, DEA involvement, patient harm, and more) across \textbf{70,000} legal case documents.}
        \resumeItem{Designed a large-scale toolkit to preprocess state medical board disciplinary records, including utilities for text chunking, token management, structured sampling, and case summarization.}
        \resumeItem{Improved model reliability through targeted DSPy optimization using an unnormalized Hamming accuracy score.}
      \resumeItemListEnd
      
      \resumeSubSubheading
      {Research Assistant $|$ \href{https://github.com/victorverma3/Undergraduate-Research/tree/main/candidate_bios}{\underline{Large-Scale Mining and Classification of State Legislator Demographics}}}{Jan 2023 - May 2024}
      \resumeItemListStart
        \resumeItem{Created a novel biographical dataset of \textbf{130,000} U.S. State Legislator candidates (1968-2022), overcoming extreme data sparsity to recover education information for \textbf{74,000} and work histories for \textbf{47,000} candidates to identify advanced degree holders and elite institution graduates.}
        \resumeItem{Architected an \textbf{NLP pipeline} to enable the zero-shot search, retrieval, and extraction of unstructured biographical data from the internet, achieving \textbf{80\%+ accuracy}, using the \textbf{Google Custom Search} and \textbf{OpenAI APIs} optimized with multithreading, retrying, PDF parsing, and error logging.}
        \resumeItem{Established a rigorous validation framework to identify invalid or hallucinated LLM outputs with a \textbf{0.80 F1} score, training \textbf{XGBoost}, \textbf{random forest}, and \textbf{neural models} on labeled validation data.}
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd
  
%-----------POSTER PRESENTATIONS-----------
\section{Poster Presentations}
          \resumeItemListStart
            \resumeItem{\textit{BU Sustainability: Water-Filling Stations}, Boston University Spark! Demo Day -- May 2024.}
            \resumeItem{\textit{Using Large Language Models for Massive Political Science Data Scraping}, Boston University Annual Undergraduate Research Symposium -- Oct 2023.}
          \resumeItemListEnd
          
%-----------HONORS AND AWARDS-----------
\section{Honors and Awards}
          \resumeItemListStart
            \resumeItem{BU Undergraduate Research Opportunities Program (UROP) Faculty Matching Grant -- Spring 2024.}
            \resumeItem{BU UROP Student Research Award -- Fall 2023, Summer 2023.}
          \resumeItemListEnd

%-----------CERTIFICATES-----------
\section{Certificates}
          \resumeItemListStart
            \resumeItem{Human Subjects Social \& Behavioral Research, CITI Program (NBER) -- valid through Sep 2029.}
          \resumeItemListEnd
          
%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{\href{https://recommendations.victorverma.com/}{\underline{Letterboxd Movie Recommendations}}} $|$ \textit{React, TypeScript, Flask, Supabase, Amazon Lightsail, Redis}}{}          
          \resumeItemListStart
            \resumeItem{Built a movie recommendation website serving \textbf{13,000+ users} across \textbf{135+ countries}, leveraging \textbf{content-based filtering} and a \textbf{random forest regressor} to suggest movies based on the user’s Letterboxd profile.}
            \resumeItem{Designed features including group recommendations, \textbf{10+} real-time statistics, exportable visualizations, a watchlist-based movie picker (recommendations or random), and compatibility between profiles.}
            \resumeItem{Reduced latency by up to \textbf{10x} using \textbf{Redis}, and improved reliability with \textbf{custom rate limiting}, automated data updates, and \textbf{CI/CD} pipelines via \textbf{5 GitHub Actions}.}
            \resumeItem{Boosted organic visibility and revenue through \textbf{SEO optimizations} and \textbf{Google AdSense} integration. }
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{\href{https://github.com/victorverma3/Movie-Review-Emotions}{\underline{Ekman Emotion Classifier}}} $|$ \textit{PyTorch, pandas, Hugging Face, Matplotlib}}{}          
          \resumeItemListStart
            \resumeItem{Developed a \textbf{feed-forward neural network} to classify text into six emotion categories, optimizing performance using SGD and grid search to achieve a \textbf{0.57 macro F1} score, and individual class scores nearing \textbf{0.70}.}
            \resumeItem{Applied the model to label the emotions expressed in \textbf{65,000+} reviews of \textbf{65} top-rated Letterboxd films, and uncovered trends between movie characteristics and viewer sentiment.}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{\href{https://github.com/ktpbu/website/tree/main/backend/assistant}{\underline{Kappa Theta Pi Lambda Chapter Website}}} $|$ \textit{Google Cloud, React, Node.js, Supabase, MongoDB}}{}          
          \resumeItemListStart
            \resumeItem{Architected a serverless \textbf{RAG agent} chatbot, integrating \textbf{Pinecone} for vector search and \textbf{Hugging Face} for inference, deployed via \textbf{Google Cloud Functions} for on-demand scalability.}
            \resumeItem{Directed a cross-functional team of \textbf{6} to deliver a \textbf{full-stack} fraternity platform featuring \textbf{Google OAuth} using \textbf{Firebase} and a centralized resource database for \textbf{111} active members.}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{\href{https://github.com/victorverma3/Electricity-Consumption}{\underline{Energy Consumption Trends across New England}}} $|$ \textit{Azure, Scikit-Learn, pandas, Power BI}}{}          
          \resumeItemListStart
            \resumeItem{Developed an end-to-end \textbf{Azure} data pipeline (\textbf{ADF}, \textbf{Synapse}, \textbf{Blob Storage}) utilizing a \textbf{medallion architecture} to process \textbf{420,000+ hours} of batch and streaming electricity data from EIA and Census APIs.}
            \resumeItem{Forecasted hourly electricity demand with a \textbf{10\% error rate} using a \textbf{Random Forest} model trained on temporal and demographic features, automated predictive workflows via scheduled \textbf{ADF pipelines}, and designed \textbf{Power BI} dashboards for stakeholder visualization.}
          \resumeItemListEnd
          
    \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages/Tools:}{ Python, SQL, JavaScript/TypeScript, Java, Git, Docker, Postman.} \\
     \textbf{AI/ML:}{ PyTorch, TensorFlow, Scikit-Learn, Hugging Face, FastMCP, LlamaIndex, DSPy, pandas, NumPy.} \\
     \textbf{Cloud/Web:}{ AWS/Azure/GCP, Node.js, Flask, FastAPI, React, PostgreSQL, Pinecone, MongoDB, Firebase, Gradio.}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}